Combinatorial Auctions

### 2015-12-17 paper.tex
afd

%%%%%%%%%% Body %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{change font size to 10}

\section{Abstract}
Combinatorial auctions are used to sell multiple goods at the same time and are particularly relevant when selling complementary and substitutive goods. In many ways combinatorial auctions are very similar to the standard auctions and matching markets that were covered in EECS 498.3 but the interdependencies between goods add aditional layers of complexity that make them very interesting to analyze. In the following paper, I will summerize and analyze part of Blumrosen and Nisan's survey on combinatorial auctions focusing on applications of the combinatorial auction, the single minded bidder, the walrasian equilibrium, bidding languages, \cite{paper}.
\todo{fix me}

@@

In a standard auction, \todo{mention how this relates to auctions in the course} there is a single good being sold to one or more players who have a demand for that good. The auctioneer determines which player is allocated the good based on which player displays the greatest demand. There are many ways for the auctioneer to coordinate the auction, such as the ascending and descending price auctions that we discussed in class. Combinatorial auctions generalize this concept of an auction by allowing multiple goods to be sold at once to players that have demands for bundles or subsets of goods. The authors, Liad Blumrosen and Noam Nisan, in their paper on Combinatorial Auctions, analyze the computational complexity of possible allocation algorithms, how to represent and communicate the value functions of bidders, and the strategic behavior of rational bidders in combinatorial auctions. In the remainder of this paper, I will be summarizing and analyzing the main arguments made by Blumrosen and Nisan.

@@

\theoremstyle{definition}
\begin{definition}{Allocation for Single Minded Bidders}
\\
\textbf{Input:} $(S'_i,v'_i)$ for each bidder $i = 1,...,n$.
\\
\textbf{Output:} The winning bids $W$ is a a subset of the bids from all of the players, $W \subseteq \{1,...,n\}$. Each winning bidder in W must posses a disjoint demand bundle from all other bundles of bidders in W: for every $i \neq j \in W$, $S'_i \cap S'_j = \emptyset$.
\end{definition}

@@

\theoremstyle{definition}
\begin{definition}{A Greedy Algorithm for Single Minded Bidders}
\\
\textbf{Initialization:} Reorder the bids s.t. $\frac{v'_1}{\sqrt{|S'_1|}} \geq \frac{v'_2}{\sqrt{|S'_2|}} \geq ... \geq \frac{v'_n}{\sqrt{|S'_n|}} $
\\
\textbf{For i = 1...n do:} if $S'_i \cap (\bigcup_{j \in W} S'_j) = \emptyset$ then $W = W \cup i$
\\
\textbf{Output:} The allocation is the set of winners, $W$. Each winning bidder is charged a price $p_i = \frac{v'_j}{\sqrt{|S'_j|/|S'_i|}}$, where j is the smallest index s.t. $S'_i \cap S'_j \neq \emptyset$, and for all $k < j, k \neq i, S'_k \cap S'_j = \emptyset$ (if no such j exists the $p_i = 0$). \todo{add citation to def} 
\end{definition}

@@

The formal proof can be found in the original paper. \todo{add citation}It is interesting to note that the approximation depends on $m$, the number of goods, but not $n$, the number of bidders. This means that for a constant number of goods the algorithm will have the same degree of approximation regardless of how many bidders there are. This property will later be of great use in the discussion on bidding languages. \todo{add ref to actual section number}

@@

\section{Ascending Auctions} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Ascending auctions

\section{Suggestions for Future Work} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%% Body %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Abstract}

Combinatorial auctions are used to sell multiple goods at the same time and are particularly relevant when selling complementary and substitutive goods. In many ways combinatorial auctions are very similar to the standard auctions and matching markets that were covered in EECS 498.3 but the interdependencies between goods add aditional layers of complexity that make them very interesting to analyze. In the following paper, I will summerize and analyze part of Blumrosen and Nisan's survey on combinatorial auctions focusing on applications of the combinatorial auction, the single minded bidder, the walrasian equilibrium, and bidding languages \cite{paper}.

@@

In a standard auction, there is a single good being sold to one or more players who have a demand for that good. The auctioneer determines which player is allocated the good based on which player displays the greatest demand. There are many ways for the auctioneer to coordinate the auction, such as the ascending and descending price auctions that we discussed in class. Combinatorial auctions generalize this concept of an auction by allowing multiple goods to be sold at once to players that have demands for bundles or subsets of goods. The authors, Liad Blumrosen and Noam Nisan, in their paper on Combinatorial Auctions, analyze the computational complexity of possible allocation algorithms, how to represent and communicate the value functions of bidders, and the strategic behavior of rational bidders in combinatorial auctions. In the remainder of this paper, I will be summarizing and analyzing the main arguments made by Blumrosen and Nisan.

@@

\theoremstyle{definition}
\begin{definition}{Allocation for Single Minded Bidders}
\\
\textbf{Input:} $(S'_i,v'_i)$ for each bidder $i = 1,...,n$.
\\
\textbf{Output:} The winning bids $W$ is a a subset of the bids from all of the players, $W \subseteq \{1,...,n\}$. Each winning bidder in W must posses a disjoint demand bundle from all other bundles of bidders in W: for every $i \neq j \in W$, $S'_i \cap S'_j = \emptyset$.

Definition from Blumrosen and Nisan's Combinatorial Auctions (a survey) pg. 271 \cite{paper}

\end{definition}

@@

\theoremstyle{definition}
\begin{definition}{A Greedy Algorithm for Single Minded Bidders}
\\
\textbf{Initialization:} Reorder the bids s.t. $\frac{v'_1}{\sqrt{|S'_1|}} \geq \frac{v'_2}{\sqrt{|S'_2|}} \geq ... \geq \frac{v'_n}{\sqrt{|S'_n|}} $
\\
\textbf{For i = 1...n do:} if $S'_i \cap (\bigcup_{j \in W} S'_j) = \emptyset$ then $W = W \cup i$
\\
\textbf{Output:} The allocation is the set of winners, $W$. Each winning bidder is charged a price $p_i = \frac{v'_j}{\sqrt{|S'_j|/|S'_i|}}$, where j is the smallest index s.t. $S'_i \cap S'_j \neq \emptyset$, and for all $k < j, k \neq i, S'_k \cap S'_j = \emptyset$ (if no such j exists the $p_i = 0$).

Definition from Blumrosen and Nisan's Combinatorial Auctions (a survey) pg. 274 \cite{paper}
\end{definition}

@@

The formal proof can be found in the original paper on page 275 \cite{paper}. It is interesting to note that the approximation depends on $m$, the number of goods, but not $n$, the number of bidders. This means that for a constant number of goods the algorithm will have the same degree of approximation regardless of how many bidders there are. This property will later be of great use in the discussion on bidding languages in section 6.

@@

\section{Conclusion and Suggestions for Future Work} %%%%%%%%%%%%%%%%%%%%%%%%%%%

Combinatorial aucitions can be applied to many applications where a set of goods needs to be auctioned off and when players have valuations that depend on bundles of goods and not just single goods, such as the London bus routes, airport runway slots, and FCC spectrum auctions. Blumerosen and Nisan outlined a survey of many theoretical consideratoins when analyzing and designing a combinatorial auction and I summerized and analyzed a few of these topics \cite{paper}. We started with the single minded bidder, whose valuation pair $(S',v')$ provided a simple way to begin analyzing the computational complextity and strategic behaiver of the auction. We next discussed walrasian equilibria, which possess market clearing prices where every player is allocated a bundle in their demand. And finally, we discussed bidding languages and how bidders can effectivly communicate their valuations to the auctioneer. While bidding langagues turned out to be the computational bottle neck of the algorithm, we still determined a way to represent very complex valuations and while still being able to apply all of the analysis and algorithms of single minded bidders.

One of the key skills that was taught in the course was the ability to simplify a general definition of a concept based on specific constraints for a particular problem. For example, finding the page rank of an undirected and connect graph. I think that it would be benificial to develop a set of simpilar, special cases of combinatorial auctions that can then be applied alone or in combination of different real world applications. By analyzing more special cases, it is then more likely that a new real world application can be applied to a special case instead of the general auction which would make running and analyzing the auction simpilar.
